Molecular dynamics simulation of synchronization in driven particles

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
moved discussion of Josephson junctions to conclusions

Experiments of colloid particles confined
in optical traps arrays or patterns 
subject to external driving forces 
have
been used to examine the microscopic dynamics
of individual particles during mode-locking \cite{Juniper2015}.
This produced step-by-step diagrams
of particle dynamics that cannot be 
imaged in electronic systems such as Josephson junctions.
%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
Thus the study of
mode-locking is a useful problem
of complex quantum mechanical systems.
Mode-locked 
colloid dynamics have been achieved in 
experiments \cite{Juniper2015, Lutz2004} and
simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
for a variety of interaction types such as 
magnetic dipoles and electric forces.
%-----------------------------------------------------------
%particle interaction types
%Particles which interact over long distances
%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
%Particles which interact over short distances include
%bubble arrays/emulsions [more systems and references].----------------------
%The presence of a modulating surface
%can modify these patterns in a variety of ways,
%changing the onset of dynamical flows,
%and the overall flow patterns.
%  adjustable strength, geometry and length scale of substrate potential
%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).

@@

\section{Synchronization in multi-particle systems}
\label{sec:sync}

@@

 We model particle interaction forces
$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
with
the Yukawa potential energy 
\begin{equation}
  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
  \label{eq:yukawa}
\end{equation}
where particle $i$ and $j$ are distance
$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
This 
screened Coulomb potential
%$E_0=2$ scales strength of repulsion
is scaled in terms of energy unit $E_0$
defined in Table ~\ref{tab:1}.
%$ = k q_1 q_2$. %[CHECK scaling/units].
$\kappa = 1/R_0$ is the screening parameter 
that describes the length scale at
which particles interact.
We fix the screening length scale $R_0$ to be $a_0$
(i.e. unity in simulation units).
In experiments charge screening is observed
due to ions in the suspending fluid and
the charges of surrounding particles
which
reduces the interaction range of individual particles. % \cite{}.
Because the particles interact over short ranges, 
the numerical models can be run efficiency
using a neighbor list algorithm
determined using a cell method.
[explain and reference!]

>>>>

Experiments of colloid particles confined
in optical traps arrays or patterns 
subject to external driving forces 
have
been used to examine the microscopic dynamics
of individual particles during mode-locking \cite{Juniper2015}.
This produced step-by-step diagrams
of particle dynamics that cannot be 
imaged in electronic systems such as Josephson junctions.
%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
Thus the study of
mode-locking is a useful problem
of complex quantum mechanical systems.

@@

\section{Synchronized particle chains}
\label{sec:sync}

Mode-locked 
colloid dynamics have been achieved in 
experiments \cite{Juniper2015, Lutz2004} and
simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
for a variety of interaction types such as 
magnetic dipoles and electric forces.
%-----------------------------------------------------------
%particle interaction types
%Particles which interact over long distances
%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
%Particles which interact over short distances include
%bubble arrays/emulsions [more systems and references].----------------------
%The presence of a modulating surface
%can modify these patterns in a variety of ways,
%changing the onset of dynamical flows,
%and the overall flow patterns.
%  adjustable strength, geometry and length scale of substrate potential
%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).

@@

 We model particle interaction forces
$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
with
the Yukawa potential $V_{ij} = U_{ij} / q$ 
\begin{equation}
  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
  \label{eq:yukawa}
\end{equation}
where particle $i$ and $j$ are distance
$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
This 
screened Coulomb potential
%$E_0=2$ scales strength of repulsion
is scaled in terms of energy unit $E_0$
defined in Table ~\ref{tab:1}.
[elaborate for students $F_{Coulomb} = = k q_1 q_2 / r^2$, check scaling/units].
$\kappa = 1/R_0$ is the screening parameter 
that describes the length scale at
which particles interact.
We fix the screening length scale $R_0$ to be $a_0$
(i.e. unity in simulation units).
In experiments charge screening is observed
due to ions in the suspending fluid and
the charges of surrounding particles
which
reduces the interaction range of individual particles. % \cite{}.
Because the particles interact over short ranges, 
the numerical models can be run efficiency
using a neighbor list algorithm
determined using a cell method.
[explain and reference!]
